Optimal Fitting of Planar Curves to Prescribed Constraints

### 2013-08-13 idp/documentation/paper.tex
continued working in idp paper

% penalizes lonely lines at the beginning or end of a page
\clubpenalty = 10000
\widowpenalty = 10000

@@

% TODO: consider splitting some illustrations into multiple figures if there is still space left at the end
% TODO: replace curvature continuity with G^2 continuity

@@

	\section{Introduction}

@@

	\section{Usability of Curve Design Tools}

@@

		\subsection{Usability of Curve Design Tools}
		\label{section:usability_curve_design_tools}

@@

		\subsection{Existing Curve Design Tools}

@@

				Applying the criteria established in section \ref{section:usability_curve_design_tools}, we conclude that the design tools for Bézier splines work sufficiently well in terms of humans trying to read and/or speak their language (criteria 2 and 3), a skill that can be acquired with some practice. Bézier splines are furthermore very simple to derive from their description, fulfilling the 5th criterion perfectly. Design tools for Bézier splines have some issues with both the fairness measure (criterion 4) and the expressiveness of the language (criterion 1), both of which shall be analyzed in the following paragraphs.

@@

				We analyze Spiro splines in terms of the criteria presented in section \ref{section:usability_curve_design_tools}. The language of Spiro splines being simply points on the curve, plus the fact that on sufficiently smooth curves, not very many of them being needed, the language is well-suited to be read and spoken by humans (criteria 2 and 3). The fairness measure leads to beautifully smooth curves that are ususally sufficiently close to what a human would expect given the control points (criterion 4). The software is also good and sufficiently quick at constructing these curves (there are some cases where the algorithm fails to find a meaningful curve, but these cases are fairly artificial and can usually be avoided when designing actual curves) and thus fulfills criterion 5 well enough.

@@

		\subsection{Specification-Based Curves}

			% with language being this important, it seems irresponsible to have it determined by the mathematical parameters of the model
			% moving from implementation detail to differential geometric specification
			% implementation section of https://code.google.com/p/kurve/wiki/Foundation
            % TODO - diagram: process of going from user input and fairness to curve
			% TODO - illustration: visually introduce point, direction, curvature with tangents and osculating circles

@@

		% segmentation, separation of segmentation and specification, global positions on curve (https://code.google.com/p/kurve/wiki/SegmentationParametrization, maybe diagram)
		% disambiguation
		% specifications
		%   position, direction and curvature
		% continuity connections
		% fixed length, constant velocity
		%   fixed length is necessary if specification positions are a fraction of the arc-length of the whole curve, otherwise, any change in the specifications may change the curve length and thus move all specifications along the curve
		% fairness
		%   derivative of projected acceleration is equal to projected jerk

@@

		% demonstrate euler spirals and bézier curves being embedded
		%   minimization of normal jerk squares prefers linear change in curvature
		% revisit examples made when analyzing Bézier splines and Spiro splines
		% a bézier node comes with 2 handles, making it 3 points, or 6 scalar values that are specified, compared to 2 scalars for a DC specification

>>>>

% penalizes orphan lines at the beginning or end of a page
\clubpenalty = 10000
\widowpenalty = 10000

@@

% TODO: consider splitting some illustrations into multiple figures if there is still space left at the end
% TODO: replace curvature continuity with G^2 continuity
% TODO: replace language with specification language

@@

	\section{Introduction}
	\label{section:introduction}

@@

	\section{Usability of Curve Design Tools}
	\label{section:usability_curve_design_tools}

@@

		\subsection{Usability Analysis}
		\label{section:usability_analysis}

@@

		\subsection{Existing Curve Design Tools}
		\label{section:existing_curve_design_tools}

@@

				Applying the criteria established in section \ref{section:usability_analysis}, we conclude that the design tools for Bézier splines work sufficiently well in terms of humans trying to read and/or speak their language (criteria 2 and 3), a skill that can be acquired with some practice. Bézier splines are furthermore very simple to derive from their description, fulfilling the 5th criterion perfectly. Design tools for Bézier splines have some issues with both the fairness measure (criterion 4) and the expressiveness of the language (criterion 1), both of which shall be analyzed in the following paragraphs.

@@

				We analyze Spiro splines in terms of the criteria presented in section \ref{section:usability_analysis}. The language of Spiro splines being simply points on the curve, plus the fact that on sufficiently smooth curves, not very many of them being needed, the language is well-suited to be read and spoken by humans (criteria 2 and 3). The fairness measure leads to beautifully smooth curves that are ususally sufficiently close to what a human would expect given the control points (criterion 4). The software is also good and sufficiently quick at constructing these curves (there are some cases where the algorithm fails to find a meaningful curve, but these cases are fairly artificial and can usually be avoided when designing actual curves) and thus fulfills criterion 5 well enough.

@@

		\subsection{Specification-Based Curves}
		\label{section:specification-based_curves}

			Seeing how the specification language and fairness measure almost completely determine all usability aspects of the resulting curve design tool, it seems unwise to choose them based on low-level mathematical aspects of the curve as is the case with Bézier splines. Spiro splines are much better in that a lot of effort was put into the fairness measure. Unfortunately, the project has set out to solve the problem of constructing interpolating splines, thereby committing to a very restricted specification language right from the start.

			We think that in order to get the best usability, using a good specification language has to be the top priority. Since it is not immediately clear which specification language is the best, the first step is to move away from the traditional explicit curve construction, and instead use a process that enables flexible construction of curves based on some specification and some fairness measure, as illustrated in figure \ref{figure:specification-based_curves}.

			\begin{figure}[htb]
				\centering
				\includegraphics[width=\textwidth]{../resources/specification-based_curves.pdf}
				\caption{Specification-Based Curves}
				\label{figure:specification-based_curves}
			\end{figure}

@@

		% segmentation, separation of segmentation and specification, global positions on curve (https://code.google.com/p/kurve/wiki/SegmentationParametrization, maybe diagram)
		% disambiguation
		% specifications
		%   differential geometric properties
		%   position, direction and curvature
		% continuity connections
		% fixed length, constant velocity
		%   fixed length is necessary if specification positions are a fraction of the arc-length of the whole curve, otherwise, any change in the specifications may change the curve length and thus move all specifications along the curve
		% fairness
		%   derivative of projected acceleration is equal to projected jerk

@@

		% demonstrate euler spirals and bézier curves being embedded
		%   minimization of normal jerk squares prefers linear change in curvature
		% take examples from demo
		% revisit examples made when analyzing Bézier splines and Spiro splines
		% a bézier node comes with 2 handles, making it 3 points, or 6 scalar values that are specified, compared to 2 scalars for a DC specification
